\documentclass{moderncv}

\moderncvtheme[green]{classic}
\arrayrulecolor{gray}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{lmodern, tabularx, multirow}

\usepackage[scale=0.78]{geometry}

\setlength{\tabcolsep}{12pt}

\name{Giorgio}{Montese}

\phone[mobile]{+39~392~070~0714}
\email{montese.giorgio@gmail.com}
\born{24 Nov 2004, Pescara}
\address{C.so Giovanni Agnelli 50}{Tourin, Italy}

\nopagenumbers

\begin{document}
\maketitle

\section{Education}
\cventry{2023--Present}{Laurea triennale in Ingegneria Aerospaziale}
		{Politecnico di Torino}{}{}{
			\textit{Graduation expected in 2026}
}

\cventry{2018--2023}{Diploma di maturità scientifica}{Liceo G. Galilei}{Pescara}{}{
	\textit{Grade: 100/100}
}

\section{Skillset}
\cvitem{\textbf{Java}}{
	7+ years of experience, advanced knowledge of
	Maven, Gradle, OOP Programming and Design Patterns.}

\cvitem{\textbf{Python}}{
	6+ years of experience, advanced knowledge of
	the standard library, Django, Flask, uWSGI, Poetry, Pipenv, Virtualenv,
	SQLAlchemy, asyncio, pytest.}

\cvitem{\textbf{C}}{
	1 year of experience, complete knowledge of the
	language, familiarity with the standard library, Makefiles, CMake,
	POSIX APIs. Operative knowledge of C++ syntax.}

\cvitem{\textbf{DevOps}}{
	3+ years of experience with Docker, including
	image creation, container orchestration, Docker Compose, Docker Swarm,
	and registries. Experience with Jenkins, Travis CI, GitHub Actions,
	and GitLab CI/CD.}

\cvitem{\textbf{Databases}}{
	5+ years of combined experience working with MySQL,
	MariaDB, SQLite, Redis, RabbitMQ, Cassandra. Advanced knowledge of
	SQL and CQL.}

\cvitem{\textbf{CAD}}{
	Basic knowledge of SolidWorks, hobby experience with
	KiCAD and AutoDesk EAGLE
}

\cvitem{\textbf{Hardware}}{
	Experience with Raspberry Pi, Arduino, ESP8266/ESP32,
	general knowledge of PCB design and manufacturing,
	digital and analog electronics, and embedded systems.
}

\section{Languages}
\cvitem{\textbf{First Language}}{Italian}
\def\arraystretch{1.7}
\begin{tabular}{p{4.5em} c | c | c | c | c}
	\cline{2-6}
	& \multicolumn{2}{c|}{\textbf{Understanding}} & \multicolumn{2}{c|}{\textbf{Speaking}} & \textbf{Writing} \\
	\cline{2-6}
	& Listening & Reading & Spoken Inter. & Spoken Prod. & \\
	\cline{2-6}
	\hfill English & C2 & C2 & C2 & C2 & C2 \\
	\cline{2-6}
\end{tabular}

\cvitem{}{\footnotesize
	Levels: A1/A2: Elementary - 
	B1/B2: Intermediate - 
	C1/C2: Proficient
}

\vspace*{\fill}
\textit{\footnotesize Autorizzo il trattamento dei miei dati personali ai sensi ai sensi del 
Decreto Legislativo 196/2003, coordinato con il Decreto Legislativo 101/2018, 
e dell'art. 13 del GDPR (Regolamento UE 2016/679)}

\end{document}
